Final Report Semester Project

### 2018-12-08 Visualizations/Draft Visualizations Template.Rmd
Cleaned up my analysis

If employees feel that their anonymity is not protected, they may be less likely to reach out for help.

@@

@@

```{r}
#Put company size in order
health$CompanySize  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
#Create Cross-tab Table
APbCS <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$CompanySize)
head(APbCS)
```

```{r}
#Create a proportions table by Row
prop.table(APbCS, 2)
```

@@

```{r}
#Do a chi-squared test
chisq.test(APbCS)
```

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small. Therefore, we cannot draw and conclusions for this test about whether these two variables are related.

####Visualization of Data

```{r}
t0 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
t0
```

@@

####Cross-tab Table

```{r}
#Add labels to tech company org
health$TLabel <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
levels = c(0, 1),
labels = c("Not primarily tech", "Primarily Tech"))
```

```{r}
#Create a crosstab table
APbT2 <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$TLabel)
head(APbT2)
```

@@

```{r}
#Create a proportions table by Row
prop.table(APbT2, 2)
```

@@

```{r}
#Do a chi-squared test
chisq.test(APbT2)
```

This chi-squared test's p value is very large. Therefore, there is likely not a relationship between these two variables.

####Visualization of Data

```{r}
#Create Visualization
t1 <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="blue")+facet_wrap(health$TLabel ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
t1
```

@@

The difference between primarily tech and non-primarily tech companies is not statistically significant in regards to anonymity policies for those seeking mental health services.  However, this may be influenced by the fact that the majority of those surveyed work for primiarily tech-oriented companies, so we do not have a large sample of those working for non-tech companies.  Furthermore, we do not know the industry that these non-tech companies are in, which means we cannot draw any firm conclusions here.  Nevertheless, in both cases, the clear majority of those surveyed indicated that they do not know  their current company's anonymity policy is towards those using mental health services.  In both cases, the next most common response to the question is that anonymity is protected for those using mental health services. As described above, the fact the majority of respondents do not know their company's anonymity policy is something that has to be addressed.

@@

This is important because if employees feel that asking for time off from work for medical leave, they may be less likely to seek the help they need.

@@

```{r}
#Modify Labels (ideal if we can get it to fit)
health$pd2 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
labels = c("Very easy (VE)", "Somewhat Easy (SE)", "Neutral (N)", "Somewhat Hard (SH)", "Very Hard (VH)", "Don't Know (DK)"))
#Modify Labels (if health$pd2 does not fit, use this as an alternate)
health$pd3 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
labels = c("VE", "SE", "N", "SH", "VH", "DK"))
```

```{r}
#Crosstab table
ELDbG <- table(health$pd2, health$gender)
ELDbG
prop.table(ELDbG, 2)
```

@@

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.  However, it potentially indicates that that the differences between genders may not be statistically significant (or we do not have enough information)

```{r}
chisq.test(ELDbG)
```

####Visualization of Data

```{r}
#Create Visualization
t2 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
t2
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

Across all genders, the most common answer is "Somewhat Easy".  Interestingly, for women the second most common answer is "Somewhat Difficult", while for men the second most common answer is "Very Easy."  For those indicating their gender falls into another category, an equal amount indicated that they felt asking for leave was very hard or provided a neutral response ("neither easy or hard"). Across all genders there is a significant group of people indicating they find it somewhat to very hard to ask for leave. That being said, there are fewer women and those from other genders participating in this survey (compared to men), which may impact our results. Furthermore, the chi-squared test indicated that the approximation may be incorrect, likely because some of the values from the table are small.

@@

```{r}
#Do the AgeGroup Variable
labs <- c(paste(seq(17, 74, by = 20), seq(37, 80, by = 20),
                sep = "-"))
health$AgeGroup <- cut(health$age, breaks = c(seq(17, 74, by = 20), Inf), labels = labs, right = FALSE)
```

```{r}
#Crosstab table
ELDbA <- table(health$pd2, health$AgeGroup)
ELDbA
#Proportions table
prop.table(ELDbA)
```

@@

```{r}
chisq.test(ELDbA)
```

We get a warning that the approximation may be incorrect, likely because some of the values from the table are small.  However, it potentially indicates that that the differences between age groups may not be statistically significant (or we do not have enough information)

####Visualization of Data

```{r}
#Create Visualization
t3 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
t3
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

The most common response for those in the 17-27 and 37-57 age ranges is that asking for leave for a mental health issue was "Somewhat Easy" and the second most common isthat asking for leave "Very Easy".  However, there is a significant number in both age groups who provided a neutral answer (e.g., neither easy or difficult) or indicated that they felt asking for leave was hard/very hard. That being said, there are few people who are 57-77 participating in this survey and there are fewer people in the 37-57 age group than the 17-27 age group. Furthermore, the chi-squared test indicated that the approximation may be incorrect, likely because some of the values from the table are small (since few people fell into the 57-77 age range).

@@

```{r}
#Crosstab table
ELDbCS <- table(health$pd2, health$CompanySize)
ELDbCS
prop.table(ELDbCS, 2)
```

@@

```{r}
chisq.test(ELDbCS)
```

Because the p value is less than .01 we can reject the null and say that we think that there is a relationship between these two variables.

####Visualization of Data

```{r}
#Create Visualization
t4 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave\nby Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
t4
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
#Modify Labels for mental health benefit provision
health$mhb2 <- factor(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.,
levels = c("I don't know", "No", "Not eligible for coverage / N/A","Yes"),
labels = c("Don't Know", "No", "Ineligible/NA", "Yes"))
```

```{r}
#Crosstab Table
ELDbMHB <- table(health$pd2, health$mhb2)
ELDbMHB
```

@@

```{r}
chisq.test(ELDbMHB)
```

Because the p value is not less than .01 we cannot reject the null. The null hypothesis is that there is no relationship between these two variables.

####Create Visualization

```{r}
t5 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(~ health$mhb2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
t5
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
ELDbEDM <- table(health$pd2, health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
ELDbEDM
```

@@

```{r}
chisq.test(ELDbEDM)
```

Because the p value is less than .01 we can reject the null and say that we think that there is a relationship between these two variables.

####Create Visualization

```{r}
t6 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication.. ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental Health\nDiscussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
t6
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

Across all categories (e.g., yes they have discussed, no they haven't, don't know), the most common response is that most recipients think it would be somewhat easy to request leave. Interestingly, for those who did not know if there has been a discussion, a large contingent also indicated they don't know how hard it would be to request leave.  For those where there has been a discussion, far fewer people say it would be hard to request leave to handle a mental illness than those who say it would be easy to very easy. For those where there has not been a discussion (which is the majority of respondents), the second most common answer is that it would be somewhat hard to request leave to hanlde a mental illness.

@@

```{r}
ELDbEOR <- table(health$pd2, health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
ELDbEOR
```

@@

Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.

```{r}
chisq.test(ELDbEOR)
```

####Create Visualization

```{r}
t7 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help. ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
t7
```
NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
ELDbPR <- table(health$pd2, health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.)
ELDbPR
prop.table(ELDbPR, 2)
```

#Revise Labels

```{r}
#Modify Labels for unsupportive response to make them shorter
health$epr <- factor(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.,
levels = c("Maybe/Not sure", "N/A", "No","Yes, I experienced", "Yes, I observed"),
labels = c("Don't Know", "N/A", "No", "Yes, experienced", "Yes, observed"))
table(health$pd2, health$epr)
```

@@

```{r}
chisq.test(ELDbPR)
```

Because the p value is less than .01 we can reject the null and say that we think that there are differences between categories.

####Create Visualization

```{r}
t8 <- ggplot(health, aes(x = health$pd3))+geom_bar()+facet_wrap(health$epr ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Experience\nwith Poor Mental health Response") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
t8
```
NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.

@@

This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a supervisor in case they need additional assistance. In addition, we may want to consider training supervisors on how to handle instances where employees reach out to them about mental health.

@@

```{r}
MHbG <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$gender)
MHbG
prop.table(MHbG, 2)
```

@@

```{r}
chisq.test(MHbG)
```

The p value is very large.  Therefore, we cannot reject the null hypothesis. The null hypothesis is that these two variables are indepdendent (no relationship between them)

####Create Visualization

```{r}
t9 <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar()+facet_grid(~ health$gender) + ggtitle("Comfort with Discussing Mental Health\nDisorder with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
t9
```

@@

```{r}
chisq.test(MHbA)
```

>>>>

This part of the analysis looks at answers to the question "Is your anonymity protected if you choose to take advantage of mental health or substance abuse treatment resources provided by your employer?" by reported company size and whether the respondent's company is primarily a tech company. This is is important because, if employees feel that their anonymity is not protected, they may be less likely to reach out for help.

@@

```{r}
#Put company size in order
health$CompanySize  = factor(health$How.many.employees.does.your.company.or.organization.have, levels=c("1-5", "6-25", "26-100", "100-500", "500-1000", "More than 1000"))
#Modify Labels for Anonymity Policies
health$AnonPolicies2 <- factor(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.,
levels = c("I don't know", "No", "Yes"),
labels = c("Don't Know", "No", "Yes"))
#Create subset
AnoymityPolicies_By_CompanySize <- table(health$AnonPolicies2, health$CompanySize)
```

@@

```{r}
#Print Cross-tab table
kable(AnoymityPolicies_By_CompanySize)
```

####Proportions Table

```{r}
#Create a proportions table by Row
kable(prop.table(AnoymityPolicies_By_CompanySize, 2))
```

@@

```{r}
#Do a chi-squared test
chisq.test(AnoymityPolicies_By_CompanySize)
```

Our null hypothesis is that there is that company size and anonymity policies are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)

We get a warning that the approximation may be incorrect, likely because some of the values from the table are less than 5 (Townsley, 2002). Therefore, we cannot draw any conclusions for this test about whether these two variables are related.

####Visualizing the Data

```{r}
#Create visualization
AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
AnoymityPolicies_By_CompanySize_Viz
```

@@

```{r}
#Add labels to tech company org question
health$TechCompany2 <- factor(health$Is.your.employer.primarily.a.tech.company.organization.,
levels = c(0, 1),
labels = c("Not primarily tech", "Primarily Tech"))
#Create a subset
AnonymityPolicies_by_TechCompany <- table(health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer., health$TechCompany2)
```

```{r}
#Print Cross-tab table
kable(AnonymityPolicies_by_TechCompany)
```

@@

```{r}
#Create a proportions table by Row
kable(prop.table(AnonymityPolicies_by_TechCompany, 2))
```

@@

```{r}
#Do a chi-squared test
chisq.test(AnonymityPolicies_by_TechCompany)
```

Our null hypothesis is that there is that company size and whether it is primarily a tech company are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002). This chi-squared test's p value is very large. Therefore, we fail to reject the null.

####Visualizing the Data

```{r}
#Create Visualization
AnonymityPolicies_by_TechCompany_viz <- ggplot(health, aes(x = health$Is.your.anonymity.protected.if.you.choose.to.take.advantage.of.mental.health.or.substance.abuse.treatment.resources.provided.by.your.employer.))+geom_bar(fill="blue")+facet_wrap(health$TechCompany2 ~ ., scales="free_y") + ggtitle("Anonymity Protections for Tech\nvs.Non-Tech Companies") + xlab("Is your anonymity protected?") + ylab("Count") + theme(axis.title=element_text(size=12))
AnonymityPolicies_by_TechCompany_viz
```

@@

The difference between primarily tech and non-primarily tech companies is not statistically significant in regards to anonymity policies for those seeking mental health services.  However, this may be influenced by the fact that the majority of those surveyed work for primiarily tech-oriented companies, so we do not have a large sample of those working for non-tech companies.  Furthermore, we do not know the industry that these non-tech companies are in, which means we cannot draw any firm conclusions here.  Nevertheless, in both cases, the clear majority of those surveyed indicated that they do not know  their current company's anonymity policy is towards those using mental health services.  In both cases, the next most common response to the question is that anonymity is protected for those using mental health services.

@@

This part of the analysis looks at answers to the question "If a mental health issue prompted you to request a medical leave from work asking for that leave would be" by respondent demographics as well as their reports of several company characteristics. This is important because if employees feel that asking for time off from work for medical leave, they may be less likely to seek the help they need.

@@

```{r}
#Modify Labels for Perceived Leave Difficulty QUestion (ideal if we can get it to fit)
health$perceivedleavediff1 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
labels = c("Very easy (VE)", "Somewhat Easy (SE)", "Neutral (N)", "Somewhat Hard (SH)", "Very Hard (VH)", "Don't Know (DK)"))
#Modify Labels for Perceived Leave Difficulty Question (if health$perceivedleavediff1 does not fit, use this as an alternate)
health$perceivedleavediff2 <- factor(health$If.a.mental.health.issue.prompted.you.to.request.a.medical.leave.from.work..asking.for.that.leave.would.be.,
levels = c("Very easy", "Somewhat easy", "Neither easy nor difficult","Somewhat difficult", "Very difficult", "I don't know"),
labels = c("VE", "SE", "N", "SH", "VH", "DK"))
#Create a subset
LeaveDiffbyGender <- table(health$perceivedleavediff1, health$gender)
```

####Crosstab Table
```{r}
#Print Crosstab
kable(LeaveDiffbyGender)
```

####Proportions Table
```{r}
#Create Proportions table
kable(prop.table(LeaveDiffbyGender, 2))
```

@@

```{r}
#Run chi-squared test
chisq.test(LeaveDiffbyGender)
```

Our null hypothesis is that there is that gender and perceived difficulty of requesting leave are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)

We get a warning that the approximation may be incorrect, likely because some of the values from the table are less than 5 (Townsley, 2002). However, the large p value potentially indicates that that the differences between genders may not be statistically significant (or we do not have enough information because of the small number of people of other genders in our dataset).

####Visualizing the Data

```{r}
#Create Visualization
LeaveDiffbyGender_Viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill="orange")+facet_wrap(health$gender ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Gender") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
LeaveDiffbyGender_Viz
```

NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

Across all genders, the most common answer is "Somewhat Easy".  Interestingly, for women the second most common answer is "Somewhat Difficult", while for men the second most common answer is "Very Easy."  For those indicating their gender falls into another category, an equal amount indicated that they felt asking for leave was very hard or provided a neutral response ("neither easy or hard"). Across all genders there is a sizable group of people indicating they find it somewhat to very hard to ask for leave, which indicates that perceived difficulty may vary by company. That being said, there are fewer women and those from other genders participating in this survey (compared to men). This means that we may not have a complete picture of the opinions of women and those who state their gender as other than male or female.

@@

```{r}
#Do the AgeGroup Variable
labs <- c(paste(seq(17, 74, by = 20), seq(37, 80, by = 20),
                sep = "-"))
health$AgeGroup <- cut(health$age, breaks = c(seq(17, 74, by = 20), Inf), labels = labs, right = FALSE)
#Create dataframe
LeaveDiffbyAge <- table(health$perceivedleavediff1, health$AgeGroup)
```

```{r}
#Print Crosstab table
kable(LeaveDiffbyAge)
```

####Proportions Table
```{r}
#Create Proportions table
kable(prop.table(LeaveDiffbyAge, 2))
```

@@

```{r}
chisq.test(LeaveDiffbyAge)
```

Our null hypothesis is that there is that age group and perceived difficulty of requesting leave are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002)

We get a warning that the approximation may be incorrect, likely because because of the small number of respondents in our survey in the 57-77 age group (Townsley, 2002). However, the large p value potentially indicates that that the differences in perceived ease of requesting leave between age may not be statistically significant (or we do not have enough information because of the small number of people in the 57-77 age group in our dataset).

####Visualizing the Data

```{r}
#Create Visualization
LeaveDiffbyAge_Viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "orange")+facet_wrap(health$AgeGroup ~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Age Group") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
LeaveDiffbyAge_Viz
```

NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

The most common response for those in the 17-27 and 37-57 age ranges is that asking for leave for a mental health issue was "Somewhat Easy" and the second most common isthat asking for leave "Very Easy".  However, there is a significant number in both age groups who provided a neutral answer (e.g., neither easy or difficult) or indicated that they felt asking for leave was hard/very hard. That being said, there are few people who are 57-77 participating in this survey and there are fewer people in the 37-57 age group than the 17-27 age group. Therefore, we may not have a complete picture of how perceived ease of requesting leave for a mental health issue may change as people age.

@@

```{r}
#Create subset
LeaveDiffbyCompanySize <- table(health$perceivedleavediff1, health$CompanySize)
```

```{r}
#Print Crosstab Table
kable(LeaveDiffbyCompanySize)
```

####Proportions Table

```{r}
kable(prop.table(LeaveDiffbyCompanySize, 2))
```

@@

```{r}
chisq.test(LeaveDiffbyCompanySize)
```

Our null hypothesis is that there is that company size and perceived difficulty of requesting leave are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002). Because the p value is less than .01 we can reject the null and say that we think that there is a relationship between these two variables.

####Visualizing the Data

```{r}
#Create Visualization
LeaveDiffbyCompanySize_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "orange")+facet_wrap(health$CompanySize~ ., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave\nby Company Size") + xlab("Perceived Difficulty Level") + ylab("Count")
LeaveDiffbyCompanySize_viz
```

NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
#Modify Labels for mental health benefit provision question
health$MHBenefit2 <- factor(health$Does.your.employer.provide.mental.health.benefits.as.part.of.healthcare.coverage.,
levels = c("I don't know", "No", "Not eligible for coverage / N/A","Yes"),
labels = c("Don't Know", "No", "Ineligible/NA", "Yes"))
#Create the subset
LeaveDiffbyMHBenefit <- table(health$perceivedleavediff1, health$MHBenefit2)
```

```{r}
#Print the Crosstab Table
kable(LeaveDiffbyMHBenefit)
```

####Proportions Table

```{r}
#Print the Crosstab Table
kable(prop.table(LeaveDiffbyMHBenefit, 2))
```

@@

```{r}
#Run Chi-squared test
chisq.test(LeaveDiffbyMHBenefit)
```

Our null hypothesis is that there is that reported mental health benefit provision and perceived difficulty of requesting leave are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002). 
Because the p value is above .01, we fail to reject the null. There does not appear to be a statistically significant relationship between the two variables.

####Visualizing the Data

```{r}
#Create Visualization
LeaveDiffbyMHBenefit_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "dark green")+facet_wrap(~ health$MHBenefit2, scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Benefit Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
LeaveDiffbyMHBenefit_viz
```

NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
#Create the subset
LeaveDiffbyMHDiscussion <- table(health$perceivedleavediff1, health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication..)
```

```{r}
#Print crosstab table
kable(LeaveDiffbyMHDiscussion)
```

####Proportions Table

```{r}
#Create proportions table
kable(prop.table(LeaveDiffbyMHDiscussion, 2))
```

@@

```{r}
#Run chi-squared test
chisq.test(LeaveDiffbyMHDiscussion)
```

Our null hypothesis is that there is that reported mental health discussion by current employer and perceived difficulty of requesting leave are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002). Because the p value is below .01, we reject the null. There appears to be a statistically significant relationship between the two variables.

####Visualizing the Data

```{r}
#Create Visualization
LeaveDiffbyMHDiscussion_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "dark green")+facet_wrap( health$Has.your.employer.ever.formally.discussed.mental.health..for.example..as.part.of.a.wellness.campaign.or.other.official.communication.. ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for \nLeave by Mental Health\nDiscussion by Employer") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
LeaveDiffbyMHDiscussion_viz
```

NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

Across all categories (e.g., yes they have discussed, no they haven't, don't know), the most common response is that most recipients think it would be somewhat easy to request leave. Interestingly, for those who did not know if there has been a discussion, a large contingent also indicated they don't know how hard it would be to request leave. For those where there has been a discussion, far fewer people say it would be hard to request leave to handle a mental illness than those who say it would be easy to very easy. For those where there has not been a discussion (which is the majority of respondents), the second most common answer is that it would be somewhat hard to request leave to handle a mental illness.  In addition, the proportion of respondents who indicated that it would be very hard to ask for leave is a lot lower in companies where it is reported that there was a mental health discussion or that it is unknown that there has been a mental health discussion compared to companies where there has not been a discussion.

@@

```{r}
#Creating the subset
LeaveDiffbyOtherMHResources <- table(health$perceivedleavediff1, health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help.)
```

```{r}
#Print the crosstab
kable(LeaveDiffbyOtherMHResources)
```

####Proportions Table

```{r}
#Create the proportions table
kable(prop.table(LeaveDiffbyOtherMHResources, 2))
```

@@

```{r}
#Run chi-squared test
chisq.test(LeaveDiffbyOtherMHResources)
```

Our null hypothesis is that there is that reported other mental health resources by current employer and perceived difficulty of requesting leave are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002). Because the p value is below .01, we reject the null. There appears to be a statistically significant relationship between the two variables.

####Visualizing the Data

```{r}
#Create visualization
LeaveDiffbyOtherMHResources_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "dark green")+facet_wrap( health$Does.your.employer.offer.resources.to.learn.more.about.mental.health.concerns.and.options.for.seeking.help. ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Mental\nHealth Resource Provision") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
LeaveDiffbyOtherMHResources_viz
```

NOTE:  VE = Very Easy, SE = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, VH = Very Hard, DK = Don't Know.

@@

```{r}
#Modify Labels for poor response to mental health issue question to make them shorter
health$expwpoorMHresponse <- factor(health$Have.you.observed.or.experienced.an.unsupportive.or.badly.handled.response.to.a.mental.health.issue.in.your.current.or.previous.workplace.,
levels = c("Maybe/Not sure", "N/A", "No","Yes, I experienced", "Yes, I observed"),
labels = c("Don't Know", "N/A", "No", "Yes, experienced", "Yes, observed"))
#Create subset
LeaveDiffbyPoorResponse <- table(health$perceivedleavediff1, health$expwpoorMHresponse)
```

```{r}
#Create table
kable(LeaveDiffbyPoorResponse)
```

####Proportions Table

```{r}
#Create proportions table
kable(prop.table(LeaveDiffbyPoorResponse, 2))
```

@@

```{r}
chisq.test(LeaveDiffbyPoorResponse)
```

Our null hypothesis is that there is that experience with a poor response to a mental health issue (current or former workplace) and perceived difficulty of requesting leave are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002). Because the p value is below .01, we reject the null. There appears to be a statistically significant relationship between the two variables.

####Visualizing the Data

```{r}
#Create Visualization
LeaveDiffbyPoorResponse_viz <- ggplot(health, aes(x = health$perceivedleavediff2))+geom_bar(fill = "red")+facet_wrap(health$expwpoorMHresponse ~., scales="free_y") + ggtitle("Perceived Difficulty of Asking for Leave by Experience\nwith Poor Mental health Response") + xlab("Perceived Difficulty Level") + ylab("Count") + theme(axis.title=element_text(size=12))
LeaveDiffbyPoorResponse_viz
```

NOTE:  E = Very Easy, S = Somewhat Easy, N = Neutral (or Neither Easy nor Difficult), SH = Somewhat Hard, H = Very Hard, D = Don't Know.

@@

This part of the analysis looks at answers to the question "Would you feel comfortable discussing a mental health disorder with your direct supervisor" by respondent demographics as well as their reports of several company characteristics. This is important because if an employee has a mental health issue, they should ideally be comfortable discussing it with a supervisor in case they need additional assistance.

@@

```{r}
#Create subset
DiscMHBossbyGender <- table(health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s.., health$gender)
```

```{r}
#Create crosstab
kable(DiscMHBossbyGender)
```

####Proportions Table

```{r}
#Create proportion table
kable(prop.table(DiscMHBossbyGender, 2))
```

@@

```{r}
#Run chi-squared test
chisq.test(DiscMHBossbyGender)
```

Our null hypothesis is that there is that reported comfort discussing mental health with supervisor and gender are independent. Our alternative hypothesis is that there is a relationship between these two variables. Because the sensitivity of this test to larger sample sizes we are setting the p value to .01 (Townsley, 2002). Because the p value is very large, we fail to reject the null. There does not appear to be a statistically significant relationship between the two variables. However, this might be influenced by the small frequencies among those who report having an other gender (Townsley, 2002).

####Visualizing the Data

```{r}
#Create visualization
DiscMHBossbyGender_viz <- ggplot(health, aes(x = health$Would.you.feel.comfortable.discussing.a.mental.health.disorder.with.your.direct.supervisor.s..))+geom_bar(fill = "orange")+facet_wrap(~ health$gender, scales="free_y") + ggtitle("Comfort with Discussing Mental Health\nDisorder with Supervisor by Gender") + xlab("Would you feel comfortable discussing a mental health\ndisorder with your supervisor?") + ylab("Count") + theme(axis.title=element_text(size=12), axis.text=element_text(size=10))
DiscMHBossbyGender_viz 
```

@@

```{r}
chisq.test(DiscMHBossbyAge)
```
